Comparing the Enriched Hits of Different Probes

### 2025-01-31 LipidProbe/EnrichedHitsComparison.qmd
eod update, messing around with 3d plots

<!-- Data wrangling, will comment out most of this when it's all done. 
Pulling the enriched hits from each probe, then making a long dataframe that can be plopped into a Venn diagram adjacent visualization -->
```{r setup, echo=FALSE,include=FALSE}
library(dplyr)
library(tidyr)
library(readr)
library(ggvenn)
library(crosstalk)
library(VennDiagram)
library(htmlwidgets)
library(plotly)
library(DT)
# # Making a big shared dataset with all of the TMT-quantified lipid probes - this is a little hand-wavey because some were run at different times... TBD if we want to keep this.
# PA_data <- read_csv("LipidProbe/DataSets/PA_HeLa_AT_2025.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

>>>>

<!-- Data wrangling, will comment out most of this when it's all done. 
Pulling the enriched hits from each probe, then making a long dataframe that can be plopped into a Venn diagram adjacent visualization -->
```{r setup, echo=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(readr)
library(ggvenn)
library(crosstalk)
library(VennDiagram)
library(htmlwidgets)
library(plotly)
library(DT)
# # Making a big shared dataset with all of the TMT-quantified lipid probes - this is a little hand-wavey because some were run at different times... TBD if we want to keep this.
# PA_data <- read_csv("LipidProbe/DataSets/PA_HeLa_AT_2025.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
